Deciding Bitvector Termination with Program Synthesis

### 2014-07-06 papers/termination/paper.tex
nudge to Cristina's nondeterminism stuff

\noindent {\bf Non-determinism.} A non-termination diagnosis procedure based on checking the satisfiability of formula {\bf [CNT]}
may fail to find a closed recurrence set for a loop $L=(G, T_u)$ when $T_u$ is non-deterministic.  
To understand the issue, imagine the following loop with an non-deterministic assignment:

\begin{lstlisting}[language=C]
while(x != 0) {
  y = nondet();
  x = x-y;
}
\end{lstlisting}

Only for certain values of \texttt{y} the loop is non-terminating.
In order to restrict the values that may be assigned to \texttt{y}, we need an assumption associated with the non-deterministic choice. 
However, such an assumption may cause a reachable state at the non-deterministic assignment to not have any successor. In such a case
the termination formula would be satisfiable, although the execution halts. This situation can be avoided by checking the existence of 
at least one successor for each reachable state at the non-deterministic assignment. Although we did put a reasonable amount of effort into it, 
we failed to come up with a formulation for the non-termination of such non-deterministic transition relations 
inside the synthesis fragment.
%formula {\bf [Nondet-CNT]} in Definition~\ref{def:nondet-cnt}.

>>>>

\noindent {\bf Non-determinism.} A non-termination diagnosis procedure based
on checking the satisfiability of formula {\bf [CNT]} may fail to find a
closed recurrence set for a loop $L=(G, T_u)$ when $T_u$ is
non-deterministic.  To understand the issue, imagine the following loop with
a non-deterministic assignment to \lstinline!y!:
%
\begin{lstlisting}[language=C]
while(x != 0) {
  y = nondet();
  x = x-y;
}
\end{lstlisting}

Only for certain choices of \texttt{y} the loop is non-terminating.  In
order to restrict the values that may be assigned to \texttt{y}, we need an
assumption associated with the non-deterministic choice.  However, such an
assumption may cause a reachable state at the non-deterministic assignment
to not have any successor.  In such a case the termination formula would be
satisfiable, although the execution halts.  This situation can be avoided by
checking the existence of at least one successor for each reachable state at
the non-deterministic assignment.  Although we did put a reasonable amount
of effort into it, we failed to come up with a formulation for the
non-termination of such non-deterministic transition relations inside the
synthesis fragment.

%formula {\bf [Nondet-CNT]} in Definition~\ref{def:nondet-cnt}.
